---
title: |
  | \LARGE Homework Assignment #1
author: |
  | \large \rm 2019150432 임효진
date: |
  | \rm \today
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    df_print: paged
mainfont: NanumBarunGothic
fontsize: 11pt
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=5, fig.height=4, fig.align ="center", out.width = "50%", warning=FALSE, message=FALSE) # global options
```

# 1
```{r}
library(ISLR)
data("College")
```

## (a)
```{r}
summary(College)
```

## (b)
```{r}
pairs(College[, 1:10])
```

## (c)
```{r}
boxplot(Outstate~Private, data=College, 
        main="Boxplot Outsate vs Private", xlab = "Private", 
        ylab = "Outstate")
```

## (d)
```{r}
Elite=rep("No", nrow(College))
Elite[College$Top10perc>50]="Yes"
Elite=as.factor(Elite)
College=data.frame(College, Elite)
summary(College$Elite)
boxplot(Outstate~Private, data=College, 
        main="Boxplot Outsate vs Elite", xlab = "Elite", 
        ylab = "Outstate")
```

## (e)
```{r}
attach(College)
par(mfrow=c(2, 2))
hist(Apps, xlab = "Apps", breaks = 1000, main = "breaks=1000")
hist(Apps, xlab = "Apps", breaks = 3000, main = "breaks=3000")
hist(Accept, xlab = "Accpet", breaks = 1000, main = "breaks=1000")
hist(Accept, xlab = "Accept", breaks = 3000, main = "breaks=3000")
```

## (f)
I will try to find the relationship between the accept rate and other variables.
```{r}
library(tidyverse)
accept_rate=Accept/Apps
College%>%mutate(accept_rate)%>%head(F)
lm_fit1=lm(accept_rate~Expend)
summary(lm_fit1)
plot(Expend, accept_rate)
lm_fit2=lm(accept_rate~Outstate)
summary(lm_fit2)
plot(Outstate, accept_rate)
```
There seems to be a statistically significant relation between the instructional expenditure per student, out-of-state tuition and acceptance rate respectively.

# 2
## (a)
```{r}
library(MASS)
data("Boston")
dim(Boston)
```
Rows represent the observations while the columns represent variables.

## (b)
```{r}
pairs(Boston)
cor(Boston)
```
Variables indus is highly correlated with nox, dis, tax. Nox is highly correlated with age and dis while lstat is highly correlated wih medv.

## (c)
```{r}
cor(Boston)[, 1] #correlation beween per capita crime rate by town
```
Variables of rad, tax, and lstat is positively correlated with crim.

## (d)
```{r}
attach(Boston)
summary(crim)
summary(tax)
summary(ptratio)
par(mfrow=c(1, 3))
hist(crim, xlab="Crime Rate")
hist(tax, xlab="Full-value property-tax rate per $10,000")
hist(ptratio, xlab="Pupil-teacher ratio by town")
```
Considering the mean and the max value of crime rate, there are suburbs in Boston that have extremely high crime rates. Also from the tax histogram the suburbs are polarized. Finally the ratio of pupil-teacher is skwed to the left which implies there are a few suburbs that have relatively low ptratio.

## (e)
```{r}
nrow(subset(Boston, chas==1))
```

## (f)
```{r}
summary(Boston$ptratio)
```

The median is 19.05 for each teacher.

## (g)
```{r}
Boston[medv==min(medv), ]
summary(Boston)
```

When comparing the overall summary and the value of suburb 399, 406 we can see that these suburbs have a relatively high crim, indus, nox, age, rad, tax, ptratio, black, and lstat. On the other hand they have a low values in variables  rm and dis.